```latex
\documentclass[11pt,a4paper,oneside]{article}
\usetikzlibrary{shapes,arrows,positioning,calc,decorations.pathmorphing,backgrounds,fit,shadows}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usetikzlibrary{shapes,arrows,positioning,backgrounds,fit,shadows}
\definecolor{Azure}{HTML}{1F618D}
\definecolor{LimeGreen}{HTML}{A0D468}
\definecolor{SkyBlue}{HTML}{8DB6CD}
\definecolor{Thistle}{HTML}{D8BFD8}
\definecolor{Gold}{HTML}{FFD700}

\geometry{a4paper, margin=1in}

\begin{document}

\section{System Architecture}
The provided content does not offer specifics on a system architecture.  Therefore, a detailed system architecture diagram is not necessary at this stage.  Further requirements gathering is needed to define the system components and their interactions.

\section{Database Design}
The provided content lacks specific details about the database schema.  To create a meaningful ER diagram, more information on the entities and their relationships is required.

\section{API Design}
The content provides a generic API flow template, but lacks details on specific APIs and endpoints.  More information is needed to customize the template meaningfully.

\section{Security Architecture}
The provided content offers a generic security architecture template.  Without specific security requirements or technologies employed, the template cannot be customized effectively.  A more detailed security analysis is required.

\section{Deployment Strategy}
The provided content includes a generic cloud deployment template.  To make it relevant, details about the specific cloud provider, infrastructure components (e.g., specific EC2 instance types), and deployment strategies are needed.  The current information is insufficient for meaningful customization.

\end{document}
```