```latex
\documentclass[11pt,a4paper,oneside]{article}
\usetikzlibrary{shapes,arrows,positioning,calc,decorations.pathmorphing,backgrounds,fit,shadows}
\usepackage{float}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{array}
\usetikzlibrary{shapes,arrows,positioning,shadows,backgrounds,fit}
\definecolor{Azure}{HTML}{F0F8FF}
\definecolor{LimeGreen}{HTML}{32CD32}
\definecolor{SkyBlue}{HTML}{87CEFA}
\definecolor{Thistle}{HTML}{D8BFD8}
\definecolor{Gold}{HTML}{FFD700}

\begin{document}

\section{System Architecture}
Since no specific architectural details are provided in the extracted content, a generic system architecture diagram would not be informative.  The provided content lacks details about specific services, databases, or user interactions.  Therefore, a customized diagram would be misleading.

\section{Database Design}
The provided content does not describe any specific database entities or relationships.  Therefore, a database design diagram cannot be created based on the available information.

\section{API Design}
The extracted content lacks details on specific API endpoints and their functionalities.  Without information on the API's intended functionality, a meaningful API flow diagram cannot be constructed.

\section{Security Architecture}
The extracted content does not provide details about specific security mechanisms beyond general security concerns.  A customized security architecture diagram cannot be created without more specific information about the implemented security features (e.g., specific WAF, authentication protocols, authorization methods).

\section{Deployment Strategy}
The provided content does not offer enough information to create a detailed and useful deployment diagram.  There is no mention of specific cloud providers, infrastructure components, or deployment strategies.

\end{document}
```